External Prior Guided Internal Prior Learning for Real Noisy Image Denoising

### 2016-11-12 CVPR2017_Review_Unified.tex
add

In our method, each local patch is extracted from a RGB image with patch size $p\times p \times 3$.\ We search the $M$ most similar patches to this local patch (including the local patch itself) in a $W\times W$ local region around it. Each patch is stretched to a patch vector $\mathbf{x}_{m}\in \mathbb{R}^{3p^{2}\times1}$ to form the PG $\{\mathbf{x}_{m}\}_{m=1}^{M}$. The mean vector of this PG is $\boldsymbol{\upmu}=\frac{1}{M}\sum_{m=1}^{M}\mathbf{x}_{m}$, and the group mean subtracted PG is defined as $\mathbf{\overline{X}}\triangleq \{\mathbf{\overline{x}}_{m}=\mathbf{x}_{m}-\boldsymbol{\upmu}\}$.

Assume we extract a number of $N$ PGs from a set of external natural images, and the $n$-th PG is $\mathbf{\overline{X}}_{n}\triangleq \{\mathbf{\overline{x}}_{n,m}\}_{m=1}^{M}, n=1,...,N$.\ A Gaussian Mixture Model (GMM) is learned to model the PG prior.\ The overall log-likelihood function is
\vspace{-2mm}
\begin{equation}\label{equ1}\vspace{-2mm}
\begin{split}
\ln\mathcal{L}=\sum_{n=1}^{N} \ln(\sum_{k=1}^{K}\pi_{k}\prod_{m=1}^{M}\mathcal{N}(\mathbf{\overline{x}}_{n,m}|\boldsymbol{\upmu}_{k},\mathbf{\Sigma}_{k})).
\end{split}
\end{equation}
The learning process is similar to the GMM learning in \cite{pgpd,epll}.\ Finally, a GMM model with $K$ Gaussian components is learned, and the learned parameters include mixture weights $\{\pi_{k}\}_{k=1}^{K}$, mean vectors $\{\boldsymbol{\upmu}_{k}\}_{k=1}^{K}$, and covariance matrices $\{\mathbf{\Sigma}_{k}\}_{k=1}^{K}$.\ Note that the mean vector of each cluster is naturally zero, i.e., $\boldsymbol{\upmu}_{k}=\mathbf{0}$.

@@

\vspace{-1mm}
\subsubsection{Comparison on Dataset \cite{crosschannel2016}}

>>>>

In our method, each local patch is extracted from a RGB image with patch size $p\times p \times 3$.\ We search the $M$ most similar patches to this local patch (including the local patch itself) in a $W\times W$ local region around it. Each patch is stretched to a patch vector $\mathbf{x}_{m}\in \mathbb{R}^{3p^{2}\times1}$ to form the PG $\{\mathbf{x}_{m}\}_{m=1}^{M}$. The mean vector of this PG is $\bm{\mu}=\frac{1}{M}\sum_{m=1}^{M}\mathbf{x}_{m}$, and the group mean subtracted PG is defined as $\mathbf{\overline{X}}\triangleq \{\mathbf{\overline{x}}_{m}=\mathbf{x}_{m}-\bm{\mu}\}$.

Assume we extract a number of $N$ PGs from a set of external natural images, and the $n$-th PG is $\mathbf{\overline{X}}_{n}\triangleq \{\mathbf{\overline{x}}_{n,m}\}_{m=1}^{M}, n=1,...,N$.\ A Gaussian Mixture Model (GMM) is learned to model the PG prior.\ The overall log-likelihood function is
\vspace{-2mm}
\begin{equation}\label{equ1}\vspace{-2mm}
\begin{split}
\ln\mathcal{L}=\sum_{n=1}^{N} \ln(\sum_{k=1}^{K}\pi_{k}\prod_{m=1}^{M}\mathcal{N}(\mathbf{\overline{x}}_{n,m}|\bm{\mu}_{k},\mathbf{\Sigma}_{k})).
\end{split}
\end{equation}
The learning process is similar to the GMM learning in \cite{pgpd,epll}.\ Finally, a GMM model with $K$ Gaussian components is learned, and the learned parameters include mixture weights $\{\pi_{k}\}_{k=1}^{K}$, mean vectors $\{\bm{\mu}_{k}\}_{k=1}^{K}$, and covariance matrices $\{\mathbf{\Sigma}_{k}\}_{k=1}^{K}$.\ Note that the mean vector of each cluster is naturally zero, i.e., $\boldsymbol{\upmu}_{k}=\mathbf{0}$.

@@

\vspace{-2mm}
\subsubsection{Comparison on Dataset \cite{crosschannel2016}}
